---
title: "Maps"
---

```{r include=F}
knitr::opts_chunk$set(out.width = "100%")
```

Maps form an important aspect of Flowminder's work. This section aims to provide general guidance, but specifically explains how these can be implemented in R, spefically highlighting how the **tmap** package can be used and how custom basemaps can be added.

# Setup

The package **tmap** provides a range of easy to use mapping features. If you want a general introduction to the package, we recommend checking the [tmap vignette](https://cran.r-project.org/web/packages/tmap/vignettes/tmap-getstarted.html).

```{r}
library(tidyverse)
library(tmap)
library(FlowmindeR)
```

**tmap** offers a fairly simple syntax for quickly building maps. It enables static and interactive maps to be produced from the same code. This can be selected by setting `tmap_mode("plot")` or `tmap_mode("view")`. Two examples are given below:

```{r}
# Interactive Graph
tmap_mode("view")
data(World)
tm_shape(World) +
  tm_polygons("HPI", id = "iso_a3", popup.vars = TRUE)
```

```{r}
# Static Graph
tmap_mode("plot")
data(World)
tm_shape(World) +
  tm_polygons("HPI")
```

# Adding Basemaps

The **ceramic package** can be used to add MapBox basemaps to plots. As advised in the [package vignettes](https://github.com/hypertidy/ceramic), when you first install the package, you will have to set the package up to your MapBox API key. You can sign up to a free account at [MapBox](https://www.mapbox.com/) which provides a generous free tier, and for personal use you should have no problem using this key as much as you need:

```{r, eval=F}
install.packages("ceramic")
Sys.setenv(MAPBOX_API_KEY = "<yourkey>")
```

Once installed, you can use the `cc_location` function to extract basemaps for a given location. This will great a raster of the outputs. To create maps in the required stlye, you can use the `base_url` function and supply `fm_mapbox_styles`. Currently, the choices are `basic`, `no borders` or `no names`:

```{r}
library(ceramic)

basemap1 <- 
cc_location(loc = cbind(-1.5, 50.99),  buffer = 2e5,
base_url = fm_mapbox_styles("basic"),
max_tiles = 9)

basemap2 <- 
cc_location(loc = cbind(-1.5, 50.99),  buffer = 2e5,
base_url = fm_mapbox_styles("no borders"),
max_tiles = 9)

basemap3 <- 
cc_location(loc = cbind(-1.5, 50.99),  buffer = 2e5,
base_url = fm_mapbox_styles("no names"),
max_tiles = 9)
```

The results are presented below:

```{r}
map1 <- 
tm_shape(basemap1) +
tm_rgb() +
tm_layout(frame = FALSE)

map2 <- 
tm_shape(basemap2) +
tm_rgb() +
tm_layout(frame = FALSE)

map3 <- 
tm_shape(basemap3) +
tm_rgb() +
tm_layout(frame = FALSE)

tmap_arrange(map1, map2, map3)
```



